---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  dpi = 300,
  fig.align = "center"
)
```

# repinion <img src='man/figures/logo.svg' align="right" height="189" />

<!-- badges: start -->
[![CodeFactor](https://www.codefactor.io/repository/github/jvieroe/repinion/badge)](https://www.codefactor.io/repository/github/jvieroe/repinion)
[![Github All Releases](https://img.shields.io/github/downloads/jvieroe/repinion/total.svg)]()
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: GPL (>= 3)](https://img.shields.io/badge/license-GPL (>= 3)-blue.svg)](https://cran.r-project.org/web/licenses/GPL (>= 3))
[![](https://img.shields.io/github/last-commit/jvieroe/repinion.svg)](https://github.com/jvieroe/repinion/commits/main)

Master branch status: [![R-CMD-check](https://github.com/jvieroe/repinion/workflows/R-CMD-check/badge.svg)](https://github.com/jvieroe/repinion/actions)
[![](https://img.shields.io/badge/devel%20version-0.1.0-dodgerblue.svg)](https://github.com/https://github.com/jvieroe/repinion)
<!-- badges: end -->


# Introduction

The purpose of `repinion` is to provide Epinion employees with `ggplot2` functionality that quickly and easily makes your graphs compliant with the Corporate Visual Identity (CVI).

`repinion` has two main functionalities:

1. tailor-made `ggplot2` themes
2. a set of custom-made color palettes for both discrete and continuous variables

## Quick example

```{r example, warning=F, message=F}
library(repinion)
library(tidyverse)

ggplot(mtcars, aes(x = wt,
                   y = mpg)) +
  geom_point(aes(color = factor(carb)),
             size = 5,
             alpha = .95) +
  geom_smooth(method = "lm",
              size = 1,
              color = grabcol("Epinion Red"),
              se = F) +
  epitheme_classic(gridlines = "both") +
  color_epi_d(palette = "main")

```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if(!require("devtools")) install.packages("devtools")
library(devtools)
devtools::install_github("jvieroe/repinion")
```

## __Epinion__ `ggplot()` themes

Use `epitheme_*()` to quickly apply a tailormode `ggplot` theme to your graphs and data visualizations. This makes them compliant with the company CVI and serves as a time-saver, especially when producing numerous plots.

`repinion` contains three Epinion themes: 

* `epitheme_classic()`, designed for most visualization purposes
  + arguments: `legend`, `gridlines`, `textcolor`
* `epitheme_map()`, a very minimalist theme designed with geospatial maps in mind
  + arguments: `legend`, `textcolor`
* `epitheme_dust()`, to a large degree similar to `epitheme_classic()` but with a warmer, dusty feel
  + arguments: `legend`, `gridlines`, `textcolor`, `background`
  
Note that you can override `theme()` elements inherent to `repinion::epitheme_*()` by specifying this in `theme(...)` _afterwards_.


```{r warning=F, message=F}
ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_dust() +
  theme(legend.position = "right")

```

Evidently, `epitheme_*()` only impacts `ggplot2::theme()` elements and not the aesthetics of your actual plot (e.g. color scales). 


## The __Epinion__ color palette 

You can apply custom-made Epinion color palettes with `repinion` through different (more or less verbose) approaches

### Using the __Epinion__ color palette 

`repinion` provides easy access to the colors from the Epinion CVI:

```{r warning=F, message=F}
getcols_epi()
getcols_epi("Epinion DarkBlue")

```

We can use these to manually change our colors by either (1) using the HEX codes provided by `repinion::getcols_epi()` directly or (2) by pasting the names into the `repinion::grabcol()` function. Both functions only accept colors in the Epinion color palette as inputs but are not sensitive to the inclusion of the Epinion prefix:


```{r warning=F, message=F}
p1 <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(am))) +
  geom_point(size = 5, alpha = .95) +
  epitheme_dust(legend = F) +
  scale_color_manual(values = c(grabcol("DarkBlue"),
                                grabcol("Red")))

p2 <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(am))) +
  geom_point(size = 5, alpha = .95) +
  epitheme_dust(legend = F) +
  scale_color_manual(values = c(grabcol("Epinion DarkBlue"),
                                grabcol("Epinion Red")))

library(patchwork)
(p1 / p2) 

```

### Applying the color palette directly

`repinion` also allows you to apply the Epinion color palette in more verbose fashion. This can be applied to both continuous and discrete variables and for both `aes(color =)` and `aes(fill =)`:

__Discrete variables__

* ```color_epi_d```: to use with the ```aes(color = x)```, where x is a ```factor``` or ```character``` variable
* ```fill_epi_d```: to use with the ```aes(fill = x)```, where x is a ```factor``` or ```character``` variable

__Continuous variables__

* ```color_epi_c```: to use with the ```aes(color = x)```, where x is a ```numeric``` or ```integer``` variable
* ```fill_epi_c```: to use with the ```aes(fill = x)```, where x is a ```numeric``` or ```integer``` variable

The main argument taken by all four functions is `reverse` which allows you to reverse the order of the color scale (default is `FALSE`). 

#### Additional arguments: `*_epi_d()`

* When mapping `color_epi_d()` or `fill_epi_d()` to a variable with __only two levels__, you can manually choose colors with the `primary` and `secondary` arguments. As with `repinion::grabcol()` colors can be specified with or without the Epinion prefix
* `repinion` contains three different discrete color palettes: `main`, `usered` __(the default)__, and `nosand`. `main` excludes Epinion Red. `nosand` excludes Warm Sand and is the preferred discrete palette when using `epitheme_dust()`

```{r warning=F, message=F}
p1 <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(vs))) +
  geom_point(size = 5, alpha = .95) +
  epitheme_dust(legend = F,
                background = TRUE) +
  color_epi_d(primary = "Red",
              secondary = "Epinion DarkBlue")

p2 <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 5, alpha = .95) +
  epitheme_dust(legend = F,
                background = TRUE) +
  color_epi_d(palette = "nosand")


library(patchwork)

p1 / p2 + 
  plot_annotation(theme = 
                    theme(plot.background = 
                            element_rect(color = NA,
                                         fill = grabcol("Epinion WarmSand"),
                                         )
                          )
                  )

```

#### Additional arguments: `*_epi_c()`

* `repinion` contains 9 different continuous color palettes:
```{r warning=F, message=F}
names(repinion::epipal_c)

```


* You choose between these with the `palette` option in `color_epi_c()` and `fill_epi_c()`

```{r warning=F, message=F}
p1 <- ggplot(mtcars, aes(x = wt, y = mpg, color = disp)) +
  geom_point(size = 5, alpha = .95) +
  epitheme_classic(legend = F, gridlines = "x") +
  color_epi_c(palette = "epigreen")

p2 <- ggplot(mtcars, aes(x = wt, y = mpg, color = disp)) +
  geom_point(size = 5, alpha = .95) +
  epitheme_classic(legend = F, gridlines = "x") +
  color_epi_c(palette = "epigreen",
              reverse = T)

p3 <- ggplot(mtcars, aes(x = wt, y = mpg, fill = disp)) +
  geom_point(size = 5, shape = 21, color = "NA", alpha = .95) +
  epitheme_classic(legend = F, gridlines = "y") +
  fill_epi_c()

p4 <- ggplot(mtcars, aes(x = wt, y = mpg, fill = disp)) +
  geom_point(size = 5, shape = 21, color = "NA", alpha = .95) +
  epitheme_classic(legend = F, gridlines = "y") +
  fill_epi_c(reverse = T)


library(patchwork)
(p1 + p2) /
  (p3 + p4)
```




#### Additional arguments

Notice that `*_epi_c()` and `*_epi_d()` inherently calls ```ggplot2::scale_*_gradientn()``` and ```ggplot2::discrete_scale()```, respectively. For that reason, additional arguments, such as ```guide```, also apply. See [```ggplot2::scale_colour_gradientn()```](https://tidyverse.github.io/ggplot2-docs/reference/scale_gradient.html "Gradient colour scales") and [```ggplot2::discrete_scale()```](https://ggplot2.tidyverse.org/reference/discrete_scale.html "Discrete scale constructor") for details on additional arguments.


# Acknowledgements

* The `R` Core Team for developing and maintaining the language
* Emil Teddy Stachurska ([emilteddy](https://github.com/emilteddy)) for inspiration through the ([epinionR](https://github.com/emilteddy/epinionR)) package
* Hadley Wickham ([hadley](https://github.com/hadley)) and the rest of the team working on the amazing ```ggplot2``` package (and, frankly, the entire ```tidyverse``` ecosystem)
* Garrick Aden-Buie ([gadenbuie](https://github.com/gadenbuie)) and Dr Simon Jackson ([drsimonj](https://github.com/drsimonj)) for inspiration
