---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  dpi = 300,
  fig.align = "center"
)
```

# repinion

<!-- badges: start -->
<!-- badges: end -->

The goal of repinion is to provide Epinion employees with `ggplot2` functionality that quickly and easily makes your graphs compliant with the Corporate Visual Identity (CVI).

## Quick example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=F, message=F}
library(repinion)
library(tidyverse)

ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_classic() +
  color_epi_d()

```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if(!require("devtools")) install.packages("devtools")
library(devtools)
devtools::install_github("jvieroe/repinion")
```

## An __Epinion__ `ggplot()` theme

Use `epitheme_*()` to quickly apply a tailormode `ggplot` theme to your graphs and data visualizations. This makes them compliant with the company CVI and serves as a time-saver, especially when producing numerous plots. At the moment, only one Epinion theme exists: `epitheme_classic()`.

`epitheme_classic()` takes three arguments as inputs:

* `legend`, specifying whether to include a legend
* `gridlines`, specifying whether to include horizontal and/or vertical gridlines
* `textcolor`, for specifying text color applied to theme text (axis labels, axis titles etc.)

```{r warning=F, message=F}
ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_classic(legend = T,
                   gridlines = "both")

```

Evidently, `epitheme_classic()` only impacts `ggplot2::theme()` elements and not the aesthetics of your actual plot. We can override `theme()` elements inherent to `repinion::epitheme_classic()` by specifying this __afterwards__:

```{r warning=F, message=F}
ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_classic() +
  theme(legend.position = "right")

```

`epitheme_classic()` only impacts `ggplot2::theme()` elements and not the aesthetics of your actual plot.


## Executing the __Epinion__ color palette 

`repinion` provides easy access to the colors from the Epinion CVI:

```{r warning=F, message=F}
getcols_epi()

getcols_epi("Epinion DarkBlue")

```

We can use these to manually change our colors, either using the HEX codes provided by `getcols_epi()` or by pasting the names into the `base::getElement()` function:


```{r warning=F, message=F}
library(gridExtra)

p1 <-
  ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_classic(legend = F) +
  scale_color_manual(values = c("#0F283C",
                                "#E8E1D5"))

p2 <-
  ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_classic(legend = F) +
  scale_color_manual(values = c(getElement(getcols_epi(), "Epinion DarkBlue"),
                                getElement(getcols_epi(), "Epinion WarmSand")))


grid.arrange(
  p1, p2,
  ncol = 2
  )

```

`repinion` also allows you to apply the Epinion color palette directly by calling `color_epi_*` or `fill_epi_*`. This can be applied to both continuous and discrete variables:

* ```color_epi_d```: to use with the ```aes(color = x)```, where x is a ```factor``` or ```character``` variable
* ```color_epi_c```: to use with the ```aes(color = x)```, where x is a ```numeric``` or ```integer``` variable
* ```fill_epi_d```: to use with the ```aes(fill = x)```, where x is a ```factor``` or ```character``` variable
* ```fill_epi_c```: to use with the ```aes(fill = x)```, where x is a ```numeric``` or ```integer``` variable

```{r warning=F, message=F}
p1 <- ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   color = factor(am))) +
  geom_point(size = 5,
             alpha = .95) +
  epitheme_classic(legend = F) +
  color_epi_d()

p2 <- ggplot(mtcars, aes(x = wt,
                   y = mpg,
                   fill = disp)) +
  geom_point(size = 5,
             shape = 21,
             color = "NA",
             alpha = .95) +
  epitheme_classic(legend = F) +
  fill_epi_c()

grid.arrange(
  p1, p2,
  ncol = 2
  )


```

